Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2012-02-16 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
add
update

\begin{frame}{Fig. 1: IC~443}
    \includegraphics[scale=0.5]{plots/four_plots_ic443_color.pdf}
\end{frame}

\begin{frame}{Fig. 11: Residual TS Map}
  \includegraphics[scale=0.5]{plots/res_tsmap_ic443_color.pdf}
\end{frame}

@@

\begin{frame}{Fig. 20: SED of RX J1713.7$-$3946}
  \includegraphics[scale=0.5]{plots/source_RX_J1713_7-3946_color.pdf}
\end{frame}

>>>>

\begin{frame}{Fig. 1 + 11: IC~443}
  Most significantly extended source
  \begin{columns}
    \column{.5\textwidth}
    \includegraphics[scale=0.35]{plots/four_plots_ic443_color.pdf}
    \column{.5\textwidth}
  \includegraphics[scale=0.35]{plots/res_tsmap_ic443_color.pdf}
  \end{columns}
\end{frame}

@@

\begin{frame}{Fig. 20: RX J1713.7$-$3946}
  \includegraphics[scale=0.5]{plots/source_RX_J1713_7-3946_color.pdf}
\end{frame}

\begin{frame}{Fig 23: Sky Map of Extended Sources}
\includegraphics[scale=0.50]{plots/allsky_extended_sources_color.pdf}
\end{frame}

\begin{frame}{Fig 24: Compare GeV and TeV Sizes}
  \includegraphics[scale=0.50]{plots/gev_vs_tev_plot_color.pdf}
\end{frame}

\begin{frame}{Fig 25: GeV and TeV Sizes (cont)}
  \includegraphics[scale=0.40]{plots/gev_vs_tev_histogram_color.pdf}
\end{frame}

\begin{frame}{Fig 26: Distribution of Spectral Indices}
  \includegraphics[scale=0.40]{plots/compare_index_2FGL_color.pdf}
\end{frame}
